How Short Lived is the Population III Epoch?

### 2010-09-07 ms.tex
Added some references and some sentences to Star Formation.

The first (Pop III) stars are metal-free and have a large
characteristic mass and suppressed fragmentation in its protostellar
collapse \citep{Abel00, ABN02, Bromm02, Yoshida03, OShea07a}.  A
fraction of these stars enrich the surrounding intergalactic medium
(IGM) when they go supernova, which can happen in stars $\lsim40~\Ms$
in Type II supernovae (SNe) or in stars roughly between 140 \Ms~and
260 \Ms~in pair-instability SNe \citep[PISNe;][]{2002ApJ...567..532H}.
The host halo and the neighboring halos are then enriched with this
ejecta.  There exists a critical metallicity that is $\sim 10^{-6}
Z_\odot$ if dust cooling is efficient \citep{refs} and $\sim 10^{-3.5}
Z_\odot$ otherwise \citep{Bromm01, 2009ApJ...691..441S}, where the gas
can cool rapidly, lowering its Jeans mass.  An intermediate
characteristic mass of $\sim10~\Ms$ can be occur if the gas cooling is
suppressed to the cosmic microwave background (CMB) temperature
\citep{Larson, Tumlinson04, 2009ApJ...691..441S}.  The resulting
Population II star cluster will thus have a lower characteristic
stellar mass than its metal-free progenitors.  In the local universe,
stars in the Milky Way halo and dwarf spheroidal (dSph) galaxies may
be connected to these first stellar clusters.  In the halo of the
Milky Way, the most metal-poor stars have a metallicity floor of [Z/H]
= ???  \citep{ref}, and in dwarf spheroidal (dSph) galaxies this floor
is a factor of 10 higher \citep{refs}.

@@

For Pop III stars, we use the same star formation model as
\citet{Abel07} and \citet{Wise08_Gal} where each star particle
represents a single star.  Instead of using a fixed stellar mass, we
randomly sampled from an IMF with a functional form of
%
\begin{equation}
\label{eqn:imf}
f(M)dM = M^{-1.3} \exp\left[-\left(\frac{M_{\rm char}}{M}\right)^{1.6}\right]
\end{equation}
%
to determine the stellar mass.  Above $M_{\rm char}$, it behaves as a
Salpeter IMF but is exponentially cutoff below that mass
\citep{Chabrier03, Clark09}.  For reproducibility, we initialize both
simulations with the same random seed and record the number of times
the random number generator \citep[Mersenne twister;][]{ref} has been
called for use when restarting the simulations.

>>>>

The first (Pop III) stars are metal-free and have a large
characteristic mass and suppressed fragmentation in its protostellar
collapse \citep{Abel00, ABN02, Bromm02_P3, Yoshida03, OShea07a}.  A
fraction of these stars enrich the surrounding intergalactic medium
(IGM) when they go supernova, which can happen in stars $\lsim40~\Ms$
in Type II supernovae (SNe) or in stars roughly between 140 \Ms~and
260 \Ms~in pair-instability SNe \citep[PISNe;][]{2002ApJ...567..532H}.
The host halo and the neighboring halos are then enriched with this
ejecta.  There exists a critical metallicity that is $\sim 10^{-6}
Z_\odot$ if dust cooling is efficient \citep{Omukai05,
  Schneider06_Frag, clark08} and $\sim 10^{-3.5} Z_\odot$ otherwise
\citep{Bromm01, 2009ApJ...691..441S}, where the gas can cool rapidly,
lowering its Jeans mass.  An intermediate characteristic mass of
$\sim10~\Ms$ can be occur if the gas cooling is suppressed to the
cosmic microwave background (CMB) temperature \citep{Larson98,
  Tumlinson07_IMF, 2009ApJ...691..441S}.  The resulting Population II
star cluster will thus have a lower characteristic stellar mass than
its metal-free progenitors.  In the local universe, stars in the Milky
Way halo and dwarf spheroidal (dSph) galaxies may be connected to
these first stellar clusters.  In the halo of the Milky Way, the most
metal-poor stars have a metallicity floor of [Z/H] = ???  \citep{ref},
and in dwarf spheroidal (dSph) galaxies this floor is a factor of 10
higher \citep{refs}.

@@

For Pop III stars, we use the same star formation model as
\citet{Abel07} and \citet{Wise08_Gal} where each star particle
represents a single star.  Instead of using a fixed stellar mass, we
randomly sampled from an IMF with a functional form of
%
\begin{equation}
\label{eqn:imf}
f(M)dM = M^{-1.3} \exp\left[-\left(\frac{M_{\rm char}}{M}\right)^{1.6}\right]
\end{equation}
to determine the stellar mass.  Above $M_{\rm char}$, it behaves as a
Salpeter IMF but is exponentially cutoff below that mass
\citep{Chabrier03, Clark09}.  For reproducibility, we initialize both
simulations with the same random seed and record the number of times
the random number generator \citep[Mersenne twister;][]{ref} has been
called for use when restarting the simulations.  Although the Pop III
star formation history (SFH) is identical for a given $N$ stars, the
Pop III SFH for a given halo can be different between the two
simulations.  This happens because the order in which halos form Pop
III stars can be altered from enhanced star formation and feedback
from nearby Pop II star clusters, as we will demonstrate in this
Letter.
